---
title: "Final story for thesis"
output: html_notebook
---

First look at the seven variables I chose in terms of box-and-jitter plots:

Autocorrelation function:

* Number of turning points
* Depth of first trough/peak pair
* Location of first turning point


```{r}
library(pastecs)

corrFiles <- list.files("/Volumes/PhD/BijelData/Batch_II_full_resolution_ED_images/Autocorrelation", pattern=".txt", full.names = TRUE)
corrFileNames <- list.files("/Volumes/PhD/BijelData/Batch_II_full_resolution_ED_images/Autocorrelation", pattern=".txt")

autoCorr <- do.call(cbind, lapply(corrFiles, read.csv, header=FALSE))
colnames(autoCorr) <- corrFileNames

exp_Data <- read.csv("/Volumes/PhD/BijelData/Bijel_Data_Cleaner_ToRead.csv", na.strings = "?")
exp_Data$Sample.Number <- as.character(exp_Data$Sample.Number)

corrFileID <- sapply(strsplit(corrFileNames,"_"), `[`,1) #`[` is a function that takes the subset of x, the input to this function is x (strsplit...) and the element of x that I want, ie the 1st one
colnames(autoCorr) <- corrFileID

rownames(exp_Data) <- exp_Data$Sample.Number
autoCorr_transpose <- data.frame(t(autoCorr))
exp_Data$Autocorrelation <- autoCorr_transpose[match(row.names(exp_Data),row.names(autoCorr_transpose)),c(1:256)]


turningPoints <- lapply(1:135, function(y) turnpoints(unlist(exp_Data$Autocorrelation[y,])))
exp_Data$Auto.Turning.Points <- turningPoints

firstTurn <- lapply(1:135, function(y) exp_Data$Auto.Turning.Points[[y]]$tppos[[1]])
exp_Data$Auto.First.Turn <- unlist(firstTurn)

peakDepth <- lapply(1:135, function(y) exp_Data$Autocorrelation[[y,exp_Data$Auto.Turning.Points[[y]]$tppos[[2]]]]-exp_Data$Autocorrelation[[y,exp_Data$Auto.Turning.Points[[y]]$tppos[[1]]]])
exp_Data$Auto.Peak.Depth <- unlist(peakDepth)


exp_Data$Auto.Num.Turns <- unlist(lapply(1:135, function(y) length(exp_Data$Auto.Turning.Points[[y]]$tppos)))

```



Radial profile:

* Average of points 29-31
* Gradient of points 1-20
* Size of biggest upward jump in the profile
* R-position of biggest upward jump in the profile

```{r}
radFiles <- list.files("/Volumes/PhD/BijelData/Batch_II_full_resolution_ED_images/Profiles", pattern=".txt", full.names = TRUE)
radFileNames <- list.files("/Volumes/PhD/BijelData/Batch_II_full_resolution_ED_images/Profiles", pattern=".txt")

radProf_data <- do.call(cbind, lapply(radFiles, read.csv, header=FALSE))
colnames(radProf_data) <- radFileNames

radFileID <- sapply(strsplit(radFileNames,"_"), `[`,1) #`[` is a function that takes the subset of x, the input to this function is x (strsplit...) and the element of x that I want, ie the 1st one
colnames(radProf_data) <- radFileID

rownames(exp_Data) <- exp_Data$Sample.Number
radProf_data_transpose <- data.frame(t(radProf_data))
exp_Data$Radial.Profile <- radProf_data_transpose[match(row.names(exp_Data),row.names(radProf_data_transpose)),c(1:256)]



r <- c(1:256)
y <- exp_Data$Radial.Profile[2:20]
lineFits <- lapply(1:135, function(n) lm(unlist(y[n,]) ~ r[2:20]))
lineCoeffs <- lapply(lineFits, function(m) m$coefficients)
lineGradients <- lapply (1:135, function(p) unname(lineCoeffs[[p]][2]))
exp_Data$Rad.Line.Gradients <- unlist(lineGradients)


avVal <- lapply(1:135, function(n) mean(unlist(exp_Data$Radial.Profile[n,29:31])))
exp_Data$Rad.Val.30 <- unlist(avVal)


jumps <- function(y,n){
  a <- exp_Data$Radial.Profile[[y,n+5]]
  b <- exp_Data$Radial.Profile[[y,n]]
  out <- a-b
  return(out)
}

#nMax <- lapply(1:135, function(y) length(exp_Data$Radial.Profile[[y]])-1)
jumpSizes <- lapply(1:135, function(y) mapply(jumps, y, 1:251))
maxJump <- lapply(1:135, function(y) max(jumpSizes[[y]]))
exp_Data$Max.Rad.Jump <- unlist(maxJump)


maxJumpX <- lapply(1:135, function(y) which.max(jumpSizes[[y]]))
exp_Data$Max.Rad.Jump.X <- unlist(maxJumpX)


```

Plot them all.
```{r}
library(ggplot2)
png(file='/Users/s1101153/Desktop/bijels1_graphs/bjp_auto-num-turns.png', width=600, height=400) 
ggplot(exp_Data, aes(x=as.factor(Bijel), y=Auto.Num.Turns, fill=Bijel)) + geom_boxplot(alpha=0.3) + geom_jitter(alpha=0.5) +  xlab("Bijel?") + ylab("Number of turning points in ACF")+theme(legend.position="none", text = element_text(size=24), axis.title = element_text(size=21))
dev.off()

png(file='/Users/s1101153/Desktop/bijels1_graphs/bjp_auto-peak-depth.png', width=600, height=400) 
ggplot(exp_Data, aes(x=as.factor(Bijel), y=Auto.Peak.Depth, fill=Bijel)) + geom_boxplot(alpha=0.3) + geom_jitter(alpha=0.5) +  xlab("Bijel?") + ylab("Depth of first ACF trough/peak pair")+theme(legend.position="none", text = element_text(size=24), axis.title = element_text(size=21))
dev.off()

png(file='/Users/s1101153/Desktop/bijels1_graphs/bjp_auto-first-turn.png', width=600, height=400) 
ggplot(exp_Data, aes(x=as.factor(Bijel), y=Auto.First.Turn, fill=Bijel)) + geom_boxplot(alpha=0.3) + geom_jitter(alpha=0.5) +
  xlab("Bijel?") + ylab("Position of first ACF turning point")+theme(legend.position="none", text = element_text(size=24), axis.title = element_text(size=21))
dev.off()

png(file='/Users/s1101153/Desktop/bijels1_graphs/bjp_rad-val-30.png', width=600, height=400) 
ggplot(exp_Data, aes(x=as.factor(Bijel), y=Rad.Val.30, fill=Bijel)) + geom_boxplot(alpha=0.3) + geom_jitter(alpha=0.5) +  xlab("Bijel?") + ylab("Average of points 29-31 of SF")+theme(legend.position="none", text = element_text(size=24), axis.title = element_text(size=21))
dev.off()

png(file='/Users/s1101153/Desktop/bijels1_graphs/bjp_rad-line-gradients.png', width=600, height=400) 
ggplot(exp_Data, aes(x=as.factor(Bijel), y=Rad.Line.Gradients, fill=Bijel)) + geom_boxplot(alpha=0.3) + geom_jitter(alpha=0.5) +  xlab("Bijel?") + ylab("Gradient of first 20 points of SF")+theme(legend.position="none", text = element_text(size=24), axis.title = element_text(size=21))
dev.off()

png(file='/Users/s1101153/Desktop/bijels1_graphs/bjp_rad-max-jump.png', width=600, height=400) 
ggplot(exp_Data, aes(x=as.factor(Bijel), y=Max.Rad.Jump, fill=Bijel)) + geom_boxplot(alpha=0.3) + geom_jitter(alpha=0.5) +  xlab("Bijel?") + ylab("Height of biggest positive jump in SF")+theme(legend.position="none", text = element_text(size=24), axis.title = element_text(size=21))
dev.off()

png(file='/Users/s1101153/Desktop/bijels1_graphs/bjp_rad-max-jump-x.png', width=600, height=400) 
ggplot(exp_Data, aes(x=as.factor(Bijel), y=Max.Rad.Jump.X, fill=Bijel)) + geom_boxplot(alpha=0.3) + geom_jitter(alpha=0.5) +  xlab("Bijel?") + ylab("Position (in r) of biggest jump in SF")+theme(legend.position="none", text = element_text(size=24), axis.title = element_text(size=21))
dev.off()

```

Plot examples of the ACF and SF too:
```{r}
x=c(1:255)
xSF=x*640.17/512
L <- 640.17
pixel_to_micron <- 2*pi/L
#example SF plots (liquid channel)
bijelSF_l <- unlist(read.csv("/Volumes/PhD/BijelData/SF_bothChannels/52ii_Image23.tif_radProf_channel0.txt"))
noBijelSF_l <- unlist(read.csv("/Volumes/PhD/BijelData/SF_bothChannels/54i_Image9.tif_radProf_channel0.txt"))
png('~/Desktop/bijels1_graphs/SFexamples_liq.png', res=300, width=1800, height=1200)
plot(xSF, bijelSF_l, type="l", lwd=2, col="red", xlab = "q (1/μm)", ylab="Structure Factor", ylim=c(0.4,2.2),cex.axis=1.5,cex.lab=2,mgp=c(2.2,0.7,0))
lines(xSF, noBijelSF_l, lwd=2)
legend("topright", legend = c("Bijel", "Non-bijel"), col=c("red", "black"), lwd=2)#, cex=1.4)
dev.off()

#example ACF plots (liquid channel)
bijelACF_l <- unlist(read.csv("/Volumes/PhD/BijelData/LiquidChannel/autoCorr/52ii_Image23.tif_autoCorr_channel0.txt"))
noBijelACF_l <- unlist(read.csv("/Volumes/PhD/BijelData/LiquidChannel/autoCorr/54i_Image9.tif_autoCorr_channel0.txt"))
x=c(1:255)
xACF=x*pixel_to_micron
png('~/Desktop/bijels1_graphs/ACFexamples_liq.png', res=300, width=1800, height=1200)
plot(xACF, bijelACF_l, type="l", lwd=2, col="red", xlab = "r (μm)", ylab="Autocorrelation Function",cex.axis=1.5,cex.lab=2,mgp=c(2.2,0.7,0))
lines(xACF, noBijelACF_l, lwd=2)
legend("topright", legend = c("Bijel", "Non-bijel"), col=c("red", "black"), lwd=2)
dev.off()
```



Now scale the data for accurate results:

```{r}
attach(exp_Data)
dat=data.frame(Auto.Num.Turns, Auto.Peak.Depth, Rad.Val.30, Rad.Line.Gradients, Max.Rad.Jump, Max.Rad.Jump.X, Auto.First.Turn)

means = unlist(lapply(1:7, function(n) mean(unlist(dat[n][]))))

datScaled = data.frame(lapply(1:7, function(n) dat[n][]*means[1]/means[n]))
datScaled$Bijel = Bijel
head(datScaled)

```

Now run decision tree (ignore this for now...)
```{r}
library(caret)
library(rpart.plot)


set.seed(1234)

trCtrl <- trainControl(method="repeatedcv", number=10, repeats = 3)
dtreeFit <- train(Bijel ~., data=datScaled, method="rpart", parms=list(split="gini"), trControl=trCtrl, tuneLength=10)

dtreeFit
prp(dtreeFit$finalModel, box.palette = "Reds", tweak=1.2, extra=101)

# table(Predict=dtreeFit$pred(datScaled), true=Bijel)

```


Now knn:
```{r}

#knn - all 7 variables
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled, method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
knn_fit
plot(knn_fit)

pairs(datScaled[-8], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled)
pairs(datScaled[-8], col=bijelPred, main="Predicted")

```


# Try removing variables


```{r}
#Auto.Num.Turns removed
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled[-1], method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
plot(knn_fit)

pairs(datScaled[2:7], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled[-1])
pairs(datScaled[2:7], col=bijelPred, main="Predicted")

```


```{r}
#Auto.Peak.Depth removed
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled[-2], method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
plot(knn_fit)

pairs(datScaled[c(1,3:7)], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled[-2])
pairs(datScaled[c(1,3:7)], col=bijelPred, main="Predicted")

```


```{r}
#Rad.Val.30 removed
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled[-3], method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
plot(knn_fit)

pairs(datScaled[c(1:2,4:7)], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled[-3])
pairs(datScaled[c(1:2,4:7)], col=bijelPred, main="Predicted")

```

```{r}
#Rad.Line.Gradients removed
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled[-4], method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
plot(knn_fit)

pairs(datScaled[c(1:3,5:7)], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled[-4])
pairs(datScaled[c(1:3,5:7)], col=bijelPred, main="Predicted")

```

```{r}
#Max.Rad.Jump removed
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled[-5], method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
plot(knn_fit)

pairs(datScaled[c(1:4,6:7)], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled[-5])
pairs(datScaled[c(1:4,6:7)], col=bijelPred, main="Predicted")

```

```{r}
#Max.Rad.Jump.X removed
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled[-6], method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
plot(knn_fit)

pairs(datScaled[c(1:5,7)], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled[-6])
pairs(datScaled[c(1:5,7)], col=bijelPred, main="Predicted")

```

```{r}
#Auto.First.Turns removed
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled[-7], method="knn", trControl=trCtrl, tuneLength=42)
error=1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
error
plot(knn_fit)

pairs(datScaled[c(1:7)], col=Bijel, main = "Data")

bijelPred <- predict(knn_fit, datScaled[-7])
pairs(datScaled[c(1:7)], col=bijelPred, main="Predicted")

```

Now remove all the variables whose removal makes the error lower than the original value of 0.2149573:

* significant change: Max.Rad.Jump.X (position 6)
* small change: Max.Rad.Jump (position 5)
* all others <0.1% decrease or an increase

```{r}
datImproved = datScaled[-6]

datImprovedSmall = datImproved[-5]
```



# F-statistic calculations

```{r}

vars <- names(datImproved)

var_fstat <- sapply(vars, function(x) {
    summary(lm(as.formula(paste(x, " ~ Bijel")), data = datImproved))$fstatistic[1]
})


sort(unlist(var_fstat), decreasing=TRUE)

vars <- names(datImprovedSmall)

var_fstat <- sapply(vars, function(x) {
    summary(lm(as.formula(paste(x, " ~ Bijel")), data = datImprovedSmall))$fstatistic[1]
})


sort(unlist(var_fstat), decreasing=TRUE)

```
stick with removing the two variables, i.e. use datImprovedSmall

# Model minimisation

```{r}

errors <- rep(NA, 5)
set.seed(1234)
knn_fit_turn5 <- train(Bijel ~., data=datImprovedSmall, method="knn", trControl=trCtrl, tuneLength=42)
errors[1]=1-knn_fit_turn5$results[row.names(knn_fit_turn5$bestTune),]$Accuracy
#plot(knn_fit_turn)

set.seed(1234)
knn_fit_turn4 <- train(Bijel ~., data=datImprovedSmall[c("Bijel", "Auto.First.Turn", "Rad.Line.Gradients", "Rad.Val.30", "Auto.Peak.Depth")], method="knn", trControl=trCtrl, tuneLength=42)
errors[2]=1-knn_fit_turn4$results[row.names(knn_fit_turn4$bestTune),]$Accuracy

set.seed(1234)
knn_fit_turn3 <- train(Bijel ~., data=datImprovedSmall[c("Bijel", "Auto.First.Turn", "Rad.Line.Gradients", "Rad.Val.30")], method="knn", trControl=trCtrl, tuneLength=42)
errors[3]=1-knn_fit_turn3$results[row.names(knn_fit_turn3$bestTune),]$Accuracy

set.seed(1234)
knn_fit_turn2 <- train(Bijel ~., data=datImprovedSmall[c("Bijel", "Auto.First.Turn", "Rad.Line.Gradients")], method="knn", trControl=trCtrl, tuneLength=42)
errors[4]=1-knn_fit_turn2$results[row.names(knn_fit_turn2$bestTune),]$Accuracy

set.seed(1234)
knn_fit_turn1 <- train(Bijel ~., data=datImprovedSmall[c("Bijel", "Auto.First.Turn")], method="knn", trControl=trCtrl, tuneLength=42)
errors[5]=1-knn_fit_turn1$results[row.names(knn_fit_turn1$bestTune),]$Accuracy


```

Plot the results

```{r}
errors
png(file='/Users/s1101153/Desktop/bijels1_graphs/error_vs_num_vars.png', width=600, height=400) 
plot(c(5,4,3,2,1), errors, xlab="Number of variables in model", ylab="Classification error", pch=19, ylim=c(.15, .2))
dev.off()

pred2 <- predict(knn_fit_turn2, data=datImprovedSmall[c("Bijel", "Auto.First.Turn", "Rad.Line.Gradients")])

png(file='/Users/s1101153/Desktop/bijels1_graphs/liquid_2vars.png', width=600, height=400)  
plot(Auto.First.Turn, Rad.Line.Gradients, col=Bijel, pch=16)
points(Auto.First.Turn, Rad.Line.Gradients, col=pred2, pch=1, cex=1.5)
dev.off()


pred1 <- predict(knn_fit_turn1, data=datImprovedSmall[c("Bijel", "Auto.First.Turn")])
set.seed(1234)
y=jitter(rep(0, each=135))
png(file='/Users/s1101153/Desktop/bijels1_graphs/liquid_result.png', width=600, height=400)  
plot(y~Auto.First.Turn, col=Bijel, pch=16, yaxt='n', xlab="Position of first turning point in Liquid Channel ACF (μm)", ylab="", log="x")
points(y~Auto.First.Turn, col=pred1, pch=1, cex=1.5)
legend("topright", legend=c("Bijel", "Non-bijel", "Pred. bijel", "Pred. non-bijel"), pch=c(16,16,1,1), col=c("red", "black", "red", "black"))
dev.off()


```




# Final model 

```{r}
final_model <- train(Bijel ~., data=datImprovedSmall[c("Bijel", "Auto.First.Turn")], method="knn", trControl=trCtrl, tuneLength=42)
errors[5]=1-knn_fit_turn1$results[row.names(knn_fit_turn1$bestTune),]$Accuracy
png(file='/Users/s1101153/Desktop/bijels1_graphs/liquid_result_k_graph.png', width=600, height=400)
plot(final_model)
dev.off()

pred_final <- predict(final_model, data=datImprovedSmall[c("Bijel", "Auto.First.Turn")])
pred_final

table(Predict=pred_final, true=Bijel)

```


# Applying the final model to new data
## First try brand new, unrelated data
First read in the new files:
```{r}
corrFilesNew <- list.files("/Volumes/PhD/BijelData/acf_new/0", pattern=".txt", full.names = TRUE)
corrFileNamesNew <- list.files("/Volumes/PhD/BijelData/acf_new/0", pattern=".txt")

autoCorrNew <- do.call(cbind, lapply(corrFilesNew, read.csv, header=FALSE))
colnames(autoCorrNew) <- corrFileNamesNew

exp_DataNew <- read.csv("/Volumes/PhD/BijelData/new_Data/Bijel_Data_Batch1.csv", na.strings = "?")
exp_DataNew$Sample.Number <- as.character(exp_DataNew$Sample.Number)

corrFileIDNew <- sapply(strsplit(corrFileNamesNew,"_"), `[`,1) #`[` is a function that takes the subset of x, the input to this function is x (strsplit...) and the element of x that I want, ie the 1st one
colnames(autoCorrNew) <- corrFileIDNew

rownames(exp_DataNew) <- exp_DataNew$Sample.Number
autoCorrNew_transpose <- data.frame(t(autoCorrNew))
exp_DataNew$Autocorrelation <- autoCorrNew_transpose[match(row.names(exp_DataNew),row.names(autoCorrNew_transpose)),c(1:256)]

num_points <- dim(exp_DataNew)[1]

turningPointsNew <- lapply(1:num_points, function(y) turnpoints(unlist(exp_DataNew$Autocorrelation[y,])))


exp_DataNew$Auto.Turning.Points <- turningPointsNew

firstTurnNew <- lapply(1:num_points, function(y) exp_DataNew$Auto.Turning.Points[[y]]$tppos[[1]])
exp_DataNew$Auto.First.Turn <- unlist(firstTurnNew)


new_for_model <- exp_DataNew[c(16,19)]

```


Now apply the final model to the new data:
```{r}
bijel_pred = predict(final_model, newdata = new_for_model)
bijel_true = new_for_model$Bijel

success_count=length(bijel_pred[bijel_pred==bijel_true])
success_rate=success_count/length(bijel_pred)
paste0("Success rate: ",100*success_rate,"%")

null_rate = length(bijel_true[bijel_true=='y'])/length(bijel_pred)


paste0("Null rate: ", 100*null_rate, "%")

table(Predict=bijel_pred, true=bijel_true)
print(data.frame(bijel_pred, bijel_true=bijel_true))
```


##Now repeat that with data more similar to the data the model was trained on:

First read in the new files (from sameSample_analysis.R in Git folder):
```{r}
bijelFilesL <- list.files("/Volumes/PhD/BijelData/sample52ii/liquid", pattern=".txt", full.names = TRUE)
bijelFileNames <- list.files("/Volumes/PhD/BijelData/sample52ii/liquid", pattern=".txt")


failFilesL <- list.files("/Volumes/PhD/BijelData/sample54i/liquid", pattern=".txt", full.names = TRUE)
failFileNames <- list.files("/Volumes/PhD/BijelData/sample54i/liquid", pattern=".txt")

autoCorrBL <- do.call(cbind, lapply(bijelFilesL, read.csv, header=FALSE))
bijelID <- sapply(strsplit(bijelFileNames,"_"), `[`,1)


bijelLabs <- rep_len("y", length(bijelFileNames))
bDat <- data.frame(Bijel=bijelLabs)
rownames(bDat) <- bijelID
bDat$Liq <- data.frame(t(autoCorrBL))



autoCorrNBL <- do.call(cbind, lapply(failFilesL, read.csv, header=FALSE))
failID <- sapply(strsplit(failFileNames,"_"), `[`,1)
#colnames(autoCorrNBL) <- colnames(autoCorrNBP) <- failID

failLabs <- rep_len("n", length(failFileNames))
nbDat <- data.frame(Bijel=failLabs)
nbDat$Liq <- data.frame(t(autoCorrNBL))


lTurnsB <- lapply(1:8, function(n) turnpoints(unlist(bDat$Liq[n,])))
firstTurnB <- lapply(1:8, function(m) lTurnsB[[m]]$tppos[1])
bDat$Auto.First.Turn <- unlist(firstTurnB)


lTurnsNB <- lapply(1:11, function(n) turnpoints(unlist(nbDat$Liq[n,])))
firstTurnNB <- lapply(1:11, function(m) lTurnsNB[[m]]$tppos[1])
nbDat$Auto.First.Turn <- unlist(firstTurnNB)

attach(bDat)
testDat1 <- data.frame(Bijel, Auto.First.Turn)

attach(nbDat)
testDat2 <- data.frame(Bijel, Auto.First.Turn)

testDat <- rbind(testDat1, testDat2)
testDat
```


Now apply the final model to the new data:
```{r}
bijel_pred = predict(final_model, newdata = testDat)
bijel_true = testDat$Bijel


length(bijel_pred)
length(bijel_true)

success_count=length(bijel_pred[bijel_pred==bijel_true])
success_count
success_rate=success_count/length(bijel_pred)
paste0("Success rate: ",100*success_rate,"%")

null_rate = 1-(length(bijel_true[bijel_true=='y'])/length(bijel_pred))


paste0("Null rate: ", 100*null_rate, "%")

table(Predict=bijel_pred, true=bijel_true)
print(data.frame(bijel_pred, bijel_true=bijel_true))
```

