---
title: 'Combined channel: final story for thesis'
output:
  html_document:
    df_print: paged
---

First read in all the data:
```{r warning=FALSE}
library(pastecs)
library(caret)
exp_Data <- read.csv("/Volumes/PhD/BijelData/Bijel_Data_Cleaner_ToRead.csv", na.strings = "?")
exp_Data$Sample.Number <- as.character(exp_Data$Sample.Number)
rownames(exp_Data) <- exp_Data$Sample.Number

partFiles <- list.files("/Volumes/PhD/BijelData/ParticleChannel/autoCorr", pattern=".txt", full.names = TRUE)
partFileNames <- list.files("/Volumes/PhD/BijelData/ParticleChannel/autoCorr", pattern=".txt")

autoCorrPart <- do.call(cbind, lapply(partFiles, read.csv, header=FALSE))
#colnames(autoCorrPart) <- partFileNames

partFileID <- sapply(strsplit(partFileNames,"_"), `[`,1) #`[` is a function that takes the subset of x, the input to this function is x (strsplit...) and the element of x that I want, ie the 1st one
colnames(autoCorrPart) <- partFileID

autoCorrPart_transpose <- data.frame(t(autoCorrPart))
exp_Data$Autocorrelation.Particle <- autoCorrPart_transpose[match(row.names(exp_Data),row.names(autoCorrPart_transpose)),c(1:256)]


liqFiles <- list.files("/Volumes/PhD/BijelData/LiquidChannel/autoCorr", pattern = ".txt", full.names = TRUE)
liqFileNames <- list.files("/Volumes/PhD/BijelData/LiquidChannel/autoCorr", pattern = ".txt")

autoCorrLiq <- do.call(cbind, lapply(liqFiles, read.csv, header=FALSE))
colnames(autoCorrLiq) <- liqFileNames

liqFileID <- sapply(strsplit(liqFileNames,"_"), `[`,1)
colnames(autoCorrLiq) <- liqFileID

autoCorrLiq_transpose <- data.frame(t(autoCorrLiq))
exp_Data$Autocorrelation.Liquid <- autoCorrLiq_transpose[match(row.names(exp_Data),row.names(autoCorrLiq_transpose)),c(1:256)]

#gradients of particle channel ACF
r <- c(1:256)
y <- exp_Data$Autocorrelation.Particle[1:20]
lineFits <- lapply(1:135, function(n) lm(unlist(y[n,]) ~ r[1:20]))
lineCoeffs <- lapply(lineFits, function(m) m$coefficients)
lineGradients <- lapply (1:135, function(p) unname(lineCoeffs[[p]][2]))
exp_Data$Particle.Gradients.20 <- unlist(lineGradients)


y2 <- exp_Data$Autocorrelation.Particle[1:10]
lineFits2 <- lapply(1:135, function(n) lm(unlist(y2[n,]) ~ r[1:10]))
lineCoeffs2 <- lapply(lineFits2, function(m) m$coefficients)
lineGradients2 <- lapply (1:135, function(p) unname(lineCoeffs2[[p]][2]))
exp_Data$Particle.Gradients.10 <- unlist(lineGradients2)


#turning point of liquid channel ACF
liquidTurns <- lapply(1:135, function(y) turnpoints(unlist(exp_Data$Autocorrelation.Liquid[y,])))
firstTurn <- lapply(1:135, function(y) liquidTurns[[y]]$tppos[1])
exp_Data$Liquid.First.Turn <- unlist(firstTurn)


```


Now scale the data for accurate results:

```{r}
attach(exp_Data)
dat=data.frame(Particle.Gradients.10, Particle.Gradients.20, Liquid.First.Turn)
means = unlist(lapply(1:3, function(n) mean(unlist(dat[n]))))
stdevs = unlist(lapply(1:3, function(n) sd(unlist(dat[n]))))
datScaled = data.frame(lapply(1:3, function(n) (dat[n]-means[n])/stdevs[n]))
datScaled$Bijel = Bijel
head(datScaled)

```



Now run knn with all variables:
```{r}
trCtrl <- trainControl(method="repeatedcv", number=10, repeats = 3)
set.seed(1234)
knn_fit <- train(Bijel ~., data=datScaled, method="knn", trControl=trCtrl, tuneLength=42)

knn_fit

```



Logistic regression all variables:
```{r}

set.seed(1234)
logRegFit <- train(Bijel ~., data=datScaled, method="glm", trControl=trCtrl)
logRegFit

```



Compare the errors:
```{r}


error_knn = 1-knn_fit$results[row.names(knn_fit$bestTune),]$Accuracy
paste0('KNN error: ', error_knn)

error_logreg = 1-logRegFit$results$Accuracy
paste0('Logistic regression error: ', error_logreg)


```


Logistic regression still has best performance. Look in detail at this result.
```{r}
logRegFit$finalModel$coefficients
```


Calculate the log odds too

```{r}

exp(logRegFit$finalModel$coefficients)

```


Calculate effect of removing each variable
```{r }

errors_logreg <- rep(NA, 7)
set.seed(1234)
logRegFitAll <- train(Bijel ~., data=datScaled, method="glm", trControl=trCtrl)
errors_logreg[1]=1-logRegFitAll$results[row.names(logRegFitAll$bestTune),]$Accuracy


logRegFit2Part <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.10', 'Particle.Gradients.20')], method="glm", trControl=trCtrl)
errors_logreg[2]=1-logRegFit2Part$results[row.names(logRegFit2Part$bestTune),]$Accuracy

logRegFit2Liq10 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.10', 'Liquid.First.Turn')], method="glm", trControl=trCtrl)
errors_logreg[3]=1-logRegFit2Liq10$results[row.names(logRegFit2Liq10$bestTune),]$Accuracy

logRegFit2Liq20 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.20', 'Liquid.First.Turn')], method="glm", trControl=trCtrl)
errors_logreg[4]=1-logRegFit2Liq20$results[row.names(logRegFit2Liq20$bestTune),]$Accuracy


logRegFit1Liq <- train(Bijel ~., data=datScaled[c('Bijel', 'Liquid.First.Turn')], method="glm", trControl=trCtrl)
errors_logreg[5]=1-logRegFit1Liq$results[row.names(logRegFit1Liq$bestTune),]$Accuracy

logRegFit1Part10 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.10')], method="glm", trControl=trCtrl)
errors_logreg[6]=1-logRegFit1Part10$results[row.names(logRegFit1Part10$bestTune),]$Accuracy

logRegFit1Part20 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.20')], method="glm", trControl=trCtrl)
errors_logreg[7]=1-logRegFit1Part20$results[row.names(logRegFit1Part20$bestTune),]$Accuracy

```

Same for knn
```{r }

errors_knn <- rep(NA, 7)
set.seed(1234)
logRegFitAll <- train(Bijel ~., data=datScaled, method="knn", trControl=trCtrl, tuneLength=42)
errors_knn[1]=1-logRegFitAll$results[row.names(logRegFitAll$bestTune),]$Accuracy


logRegFit2Part <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.10', 'Particle.Gradients.20')], method="knn", trControl=trCtrl, tuneLength=42)
errors_knn[2]=1-logRegFit2Part$results[row.names(logRegFit2Part$bestTune),]$Accuracy

logRegFit2Liq10 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.10', 'Liquid.First.Turn')], method="knn", trControl=trCtrl, tuneLength=42)
errors_knn[3]=1-logRegFit2Liq10$results[row.names(logRegFit2Liq10$bestTune),]$Accuracy

logRegFit2Liq20 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.20', 'Liquid.First.Turn')], method="knn", trControl=trCtrl, tuneLength=42)
errors_knn[4]=1-logRegFit2Liq20$results[row.names(logRegFit2Liq20$bestTune),]$Accuracy


logRegFit1Liq <- train(Bijel ~., data=datScaled[c('Bijel', 'Liquid.First.Turn')], method="knn", trControl=trCtrl, tuneLength=42)
errors_knn[5]=1-logRegFit1Liq$results[row.names(logRegFit1Liq$bestTune),]$Accuracy

logRegFit1Part10 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.10')], method="knn", trControl=trCtrl, tuneLength=42)
errors_knn[6]=1-logRegFit1Part10$results[row.names(logRegFit1Part10$bestTune),]$Accuracy

logRegFit1Part20 <- train(Bijel ~., data=datScaled[c('Bijel', 'Particle.Gradients.20')], method="knn", trControl=trCtrl, tuneLength=42)
errors_knn[7]=1-logRegFit1Part20$results[row.names(logRegFit1Part20$bestTune),]$Accuracy

```


Plot this:
```{r }
errors_logreg
png(file='/Users/s1101153/Desktop/bijels2_graphs/error_vs_num_vars_combo.png', width=600, height=400) 
plot(c(3,2,2,2,1,1,1), errors_logreg, xlab="Number of variables in model", ylab="Classification error", pch=1)
points(c(3,2,2,2,1,1,1), errors_knn, xlab="Number of variables in model", ylab="Classification error", pch=1, col=2)
legend("topright", legend=c("KNN", "Logistic regression"), pch=19, col=c("red", "black"))
dev.off()
```

Settle on the final model:
```{r }
#attach(exp_Data)
finalDat=data.frame(Particle.Gradients.20, Particle.Gradients.10, Liquid.First.Turn, Bijel)
means = unlist(lapply(1:3, function(n) mean(unlist(dat[n]))))
stdevs = unlist(lapply(1:3, function(n) sd(unlist(dat[n]))))
finalDat_scaled = data.frame(lapply(1:3, function(n) (finalDat[n]-means[n])/stdevs[n]))
finalDat_scaled$Bijel = Bijel
summary(finalDat_scaled)

set.seed(1234)
trCtrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)

set.seed(1234)
final_model <- train(Bijel~., data=finalDat_scaled, method="glm", trControl=trCtrl)

table(Predict=predict(final_model), true=finalDat_scaled$Bijel)
```



Plot the predictions of the best model (using the unscaled version of the variable for the plot axes):

```{r message=FALSE}
#attach(exp_Data)
#final_model = logRegFitAll
#pred = predict(final_model, data=datScaled)
#pred
#pred==Bijel

png('/Users/s1101153/Desktop/bijels2_graphs/results_final.png', res=300, width=4200, height=1400)
par(mfrow=c(1,3), ps=20, mar=c(5,5,2,1), cex=1, cex.axis=0.8)
plot(datScaled$Particle.Gradients.10, datScaled$Liquid.First.Turn, col=datScaled$Bijel, pch=16, xlab="Particle ACF 10-point gradient", ylab="Liquid ACF turning point")
points(datScaled$Particle.Gradients.10, datScaled$Liquid.First.Turn, col=predict(final_model), pch=1, cex=1.5)
legend("topleft", legend=c("Bijel", "Non-bijel", "Pred bijel", "Pred non-bijel"), pch=c(16,16,1,1), col=c("red", "black", "red", "black"), cex=0.7)

plot(datScaled$Particle.Gradients.20, datScaled$Liquid.First.Turn, col=datScaled$Bijel, pch=16, xlab="Particle ACF 20-point gradient", ylab="Liquid ACF turning point")
points(datScaled$Particle.Gradients.20, datScaled$Liquid.First.Turn, col=predict(final_model), pch=1, cex=1.5)
legend("topleft", legend=c("Bijel", "Non-bijel", "Pred bijel", "Pred non-bijel"), pch=c(16,16,1,1), col=c("red", "black", "red", "black"), cex=0.7)

plot(datScaled$Particle.Gradients.10, datScaled$Particle.Gradients.20, col=datScaled$Bijel, pch=16, xlab="Particle ACF 10-point gradient", ylab="Particle ACF 20-point gradient")
points(datScaled$Particle.Gradients.10, datScaled$Particle.Gradients.20, col=predict(final_model), pch=1, cex=1.5)
legend("topleft", legend=c("Bijel", "Non-bijel", "Pred bijel", "Pred non-bijel"), pch=c(16,16,1,1), col=c("red", "black", "red", "black"), cex=0.7)

dev.off()

```

Plot the 3rd panel alone to compare to the particle channel result
```{r}
png('/Users/s1101153/Desktop/bijels2_graphs/results_combo_part_comp.png', width=600, height=400)
plot(datScaled$Particle.Gradients.10, datScaled$Particle.Gradients.20, col=datScaled$Bijel, pch=16, xlab="Particle ACF 10-point gradient", ylab="Particle ACF 20-point gradient")
points(datScaled$Particle.Gradients.10, datScaled$Particle.Gradients.20, col=predict(final_model), pch=1, cex=1.5)
abline(a=-0.1814074, b=1.135985, col='blue', lty=2)
legend("topleft", legend=c("Bijel", "Non-bijel", "Pred bijel (combined model)", "Pred non-bijel (combined model)", "Particle channel model decision boundary"), pch=c(16,16,1,1,NA), lty=c(NA,NA,NA,NA,2), col=c("red", "black", "red", "black", "blue"))

dev.off()
```

Plot to compare to liquid model
```{r}
png('/Users/s1101153/Desktop/bijels2_graphs/results_for_liq_comp.png', width=600, height=400)
plot(exp_Data$Liquid.First.Turn, exp_Data$Particle.Gradients.10, col=exp_Data$Bijel, pch=16, xlab="Liquid ACF first turning point", ylab="Particle ACF 10-point gradient", log='x')
points(exp_Data$Liquid.First.Turn, exp_Data$Particle.Gradients.10, col=predict(final_model), pch=1, cex=1.5)
legend("bottomright", legend=c("Bijel", "Non-bijel", "Pred bijel", "Pred non-bijel"), pch=c(16,16,1,1), col=c("red", "black", "red", "black"))

dev.off()
```



Table of the results:

```{r }
#table(Predict=predict(final_model), true=datScaled$Bijel)
```


# Applying the final model to new data
## First try brand new, unrelated data
First read in the new files:
```{r }
exp_DataNew <- read.csv("/Volumes/PhD/BijelData/new_Data/Bijel_Data_Batch1.csv", na.strings = "?")
exp_DataNew$Sample.Number <- as.character(exp_DataNew$Sample.Number)
rownames(exp_DataNew) <- exp_DataNew$Sample.Number




# liquid channel
corrFilesNewL <- list.files("/Volumes/PhD/BijelData/acf_new/0", pattern=".txt", full.names = TRUE)
corrFileNamesNewL <- list.files("/Volumes/PhD/BijelData/acf_new/0", pattern=".txt")
corrFileIDNewL <- sapply(strsplit(corrFileNamesNewL,"_"), `[`,1) #`[` is a function that takes the subset of x, the input to this function is x (strsplit...) and the element of x that I want, ie the 1st one

autoCorrNewL <- do.call(cbind, lapply(corrFilesNewL, read.csv, header=FALSE))
#colnames(autoCorrNewL) <- corrFileNamesNewL

colnames(autoCorrNewL) <- corrFileIDNewL

autoCorrNewL_transpose <- data.frame(t(autoCorrNewL))
exp_DataNew$Liq <- autoCorrNewL_transpose[match(row.names(exp_DataNew),row.names(autoCorrNewL_transpose)),c(1:256)]


# particle channel
corrFilesNewP <- list.files("/Volumes/PhD/BijelData/acf_new/1", pattern=".txt", full.names = TRUE)
corrFileNamesNewP <- list.files("/Volumes/PhD/BijelData/acf_new/1", pattern=".txt")
corrFileIDNewP <- sapply(strsplit(corrFileNamesNewP,"_"), `[`,1) #`[` is a function that takes the subset of x, the input to this function is x (strsplit...) and the element of x that I want, ie the 1st one

autoCorrNewP <- do.call(cbind, lapply(corrFilesNewP, read.csv, header=FALSE))
#colnames(autoCorrNewP) <- corrFileNamesNewP

colnames(autoCorrNewP) <- corrFileIDNewP

autoCorrNewP_transpose <- data.frame(t(autoCorrNewP))
exp_DataNew$Part <- autoCorrNewP_transpose[match(row.names(exp_DataNew),row.names(autoCorrNewP_transpose)),c(1:256)]



num_points <- dim(exp_DataNew)[1]

#particle variables
r <- c(1:256)
y <- exp_DataNew$Part[1:20]
lineFits <- lapply(1:num_points, function(n) lm(unlist(y[n,]) ~ r[1:20]))
lineCoeffs <- lapply(lineFits, function(m) m$coefficients)
lineGradients <- lapply (1:num_points, function(p) unname(lineCoeffs[[p]][2]))
exp_DataNew$Particle.Gradients.20 <- unlist(lineGradients)


y2 <- exp_DataNew$Part[1:10]
lineFits2 <- lapply(1:num_points, function(n) lm(unlist(y2[n,]) ~ r[1:10]))
lineCoeffs2 <- lapply(lineFits2, function(m) m$coefficients)
lineGradients2 <- lapply (1:num_points, function(p) unname(lineCoeffs2[[p]][2]))
exp_DataNew$Particle.Gradients.10 <- unlist(lineGradients2)

#liquid variables
turningPointsNew <- lapply(1:num_points, function(y) turnpoints(unlist(exp_DataNew$Liq[y,])))


exp_DataNew$Liquid.Turning.Points <- turningPointsNew

firstTurnNew <- lapply(1:num_points, function(y) exp_DataNew$Liquid.Turning.Points[[y]]$tppos[[1]])
exp_DataNew$Liquid.First.Turn <- unlist(firstTurnNew)



detach(exp_Data)
attach(exp_DataNew)
new_for_model <- data.frame(Particle.Gradients.20, Particle.Gradients.10, Liquid.First.Turn)
head(new_for_model)
new_for_model = data.frame(lapply(1:3, function(n) (new_for_model[n]-means[n])/stdevs[n]))
new_for_model$Bijel = exp_DataNew$Bijel
dim(new_for_model)
```


Now apply the final model to the new data:
```{r }
bijel_pred = predict(final_model, newdata = new_for_model)
bijel_true = new_for_model$Bijel

success_count=length(bijel_pred[bijel_pred==bijel_true])
success_rate=success_count/length(bijel_pred)
paste0("Success rate: ",100*success_rate,"%")

null_rate = length(bijel_true[bijel_true=='y'])/length(bijel_pred)


paste0("Null rate: ", 100*null_rate, "%")

table(Predict=bijel_pred, true=bijel_true)
print(data.frame(bijel_pred, bijel_true=bijel_true))
```


##Now repeat that with data more similar to the data the model was trained on:

First read in the new files (from sameSample_analysis.R in Git folder):
```{r }

bijelFilesL <- list.files("/Volumes/PhD/BijelData/sample52ii/liquid", pattern=".txt", full.names = TRUE)
bijelFileNames <- list.files("/Volumes/PhD/BijelData/sample52ii/liquid", pattern=".txt")
bijelFilesP <- list.files("/Volumes/PhD/BijelData/sample52ii/particle", pattern=".txt", full.names = TRUE)


failFilesL <- list.files("/Volumes/PhD/BijelData/sample54i/liquid", pattern=".txt", full.names = TRUE)
failFileNames <- list.files("/Volumes/PhD/BijelData/sample54i/liquid", pattern=".txt")
failFilesP <- list.files("/Volumes/PhD/BijelData/sample54i/particle", pattern=".txt", full.names = TRUE)

autoCorrBL <- do.call(cbind, lapply(bijelFilesL, read.csv, header=FALSE))
autoCorrBP <- do.call(cbind, lapply(bijelFilesP, read.csv, header=FALSE))
bijelID <- sapply(strsplit(bijelFileNames,"_"), `[`,1)
#colnames(autoCorrBL) <- colnames(autoCorrBP) <- bijelID


bijelLabs <- rep_len("y", length(bijelFileNames))
bDat <- data.frame(Bijel=bijelLabs)
rownames(bDat) <- bijelID
bDat$Liq <- data.frame(t(autoCorrBL))
bDat$Par <- data.frame(t(autoCorrBP))


autoCorrNBL <- do.call(cbind, lapply(failFilesL, read.csv, header=FALSE))
autoCorrNBP <- do.call(cbind, lapply(failFilesP, read.csv, header=FALSE))
failID <- sapply(strsplit(failFileNames,"_"), `[`,1)
#colnames(autoCorrNBL) <- colnames(autoCorrNBP) <- failID

failLabs <- rep_len("n", length(failFileNames))
nbDat <- data.frame(Bijel=failLabs)
#rownames(nbDat) <- failID
nbDat$Liq <- data.frame(t(autoCorrNBL))
nbDat$Par <- data.frame(t(autoCorrNBP))


yB <- bDat$Par[1:20]
lineFitsB <- lapply(1:8, function(n) lm(unlist(yB[n,]) ~ r[1:20]))
lineCoeffsB <- lapply(lineFitsB, function(m) m$coefficients)
lineGradientsB <- lapply(1:8, function(p) unname(lineCoeffsB[[p]][2]))
bDat$Particle.Gradients.20 <- unlist(lineGradientsB)

yB2 <- bDat$Par[1:10]
lineFitsB2 <- lapply(1:8, function(n) lm(unlist(yB2[n,]) ~ r[1:10]))
lineCoeffsB2 <- lapply(lineFitsB2, function(m) m$coefficients)
lineGradientsB2 <- lapply(1:8, function(p) unname(lineCoeffsB2[[p]][2]))
bDat$Particle.Gradients.10 <- unlist(lineGradientsB2)

lTurnsB <- lapply(1:8, function(n) turnpoints(unlist(bDat$Liq[n,])))
firstTurnB <- lapply(1:8, function(m) lTurnsB[[m]]$tppos[1])
bDat$Liquid.First.Turn <- unlist(firstTurnB)


yNB <- nbDat$Par[1:20]
lineFitsNB <- lapply(1:11, function(n) lm(unlist(yNB[n,]) ~ r[1:20]))
lineCoeffsNB <- lapply(lineFitsNB, function(m) m$coefficients)
lineGradientsNB <- lapply(1:11, function(p) unname(lineCoeffsNB[[p]][2]))
nbDat$Particle.Gradients.20 <- unlist(lineGradientsNB)

yNB2 <- nbDat$Par[1:10]
lineFitsNB2 <- lapply(1:11, function(n) lm(unlist(yNB2[n,]) ~ r[1:10]))
lineCoeffsNB2 <- lapply(lineFitsNB2, function(m) m$coefficients)
lineGradientsNB2 <- lapply(1:11, function(p) unname(lineCoeffsNB2[[p]][2]))
nbDat$Particle.Gradients.10 <- unlist(lineGradientsNB2)

lTurnsNB <- lapply(1:11, function(n) turnpoints(unlist(nbDat$Liq[n,])))
firstTurnNB <- lapply(1:11, function(m) lTurnsNB[[m]]$tppos[1])
nbDat$Liquid.First.Turn <- unlist(firstTurnNB)
detach(exp_DataNew)
attach(bDat)
testDat1 <- data.frame(Particle.Gradients.20, Particle.Gradients.10, Liquid.First.Turn, Bijel)

detach(bDat)
attach(nbDat)
testDat2 <- data.frame(Particle.Gradients.20, Particle.Gradients.10, Liquid.First.Turn, Bijel)

testDat <- rbind(testDat1, testDat2)
#!!!!!!!!!!
testDat_scaled <- data.frame(lapply(1:3, function(n) (testDat[n]-means[n])/stdevs[n]))
testDat_scaled$Bijel <- testDat$Bijel
predict(final_model, newdata = testDat_scaled)





bijel_pred = predict(final_model, newdata = testDat_scaled)
bijel_true = testDat_scaled$Bijel


length(bijel_pred)
length(bijel_true)

success_count=length(bijel_pred[bijel_pred==bijel_true])
success_count
success_rate=success_count/length(bijel_pred)
paste0("Success rate: ",100*success_rate,"%")

null_rate = 1-(length(bijel_true[bijel_true=='y'])/length(bijel_pred))


paste0("Null rate: ", 100*null_rate, "%")

table(Predict=bijel_pred, true=bijel_true)

```


Finally, do a ROC curve and a histogram of random labels. First the histogram:

```{r}
# random labelling histogram
true_error = 1-(final_model$results[row.names(final_model$bestTune),]$Accuracy)
num_samps = 1000
set.seed(1234)
bijelLabs <- replicate(num_samps, sample(c("y","n"), 135, replace=TRUE, prob=c(.68, .32)))
bijelLabs[,1]

errors <- vector("list", num_samps)
for(i in c(1:num_samps)){
 dat=data.frame(datScaled$Particle.Gradients.20, datScaled$Particle.Gradients.10, datScaled$Liquid.First.Turn, y=bijelLabs[,i])
 set.seed(1234)
 fit <- train(y ~., data=dat, method="glm", trControl=trCtrl)
 errors[i] <- 1-fit$results$Accuracy
}

errorDF = data.frame(c(1:num_samps), data.frame(unlist(errors)))
png('/Users/s1101153/Desktop/bijels2_graphs/random_hist_combo.png', res=300, height=1400, width=1600)
ggplot(data=errorDF, aes(errorDF$unlist.errors.)) + geom_histogram()  + scale_y_continuous(expand=c(0,0),limits=c(0,120))+ scale_x_continuous(expand=c(0,0),limits=c(0.1,0.45)) + geom_vline(aes(xintercept=true_error, linetype="Model error"), show.legend= TRUE, color="purple") + xlab("Error for randomly labelled samples") + ylab("Frequency") + theme(legend.title = element_blank(), text = element_text(size=18), axis.title = element_text(size=18))
dev.off()
```

ROC (https://cran.r-project.org/web/packages/plotROC/vignettes/examples.html):
```{r}
resultDat <- data.frame(Bijel=datScaled$Bijel, comboPred=predict(final_model, type="prob")[[2]])
resultDat$Bijel


library(plotROC)
basicplot <- ggplot(resultDat, aes(d=Bijel, m=comboPred)) +geom_roc(cutoffs.at=c(0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0), labelsize=4, alpha=0.7)

png('~/Desktop/bijels2_graphs/ROC_combo.png', res=300, width=1800, height=1200)
basicplot + xlab('False positive fraction') + ylab('True positive fraction') + annotate("text", x = .75, y = .25,label = paste("AUC =", round(calc_auc(basicplot)$AUC, 2))) #+ ggtitle('ROC curve for particle channel model')
dev.off()

```


